Image Processing and geometrical analysis for profile detection during P-Gas Metal Arc Welding

### 2011-03-25 articles/MIG/paper-drop_v1.tex

\section{Image processing} 
\label{ image_processing}

@@

A multipurpose image processing library was developed 
and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different 
welding objects such as Macro drop, droplets and weld pool.
The library can manage
different kinds of image acquisition (optical setup). 
erCv is assembled in a oriented object C++ language.
Then,  erCv is a scalable 
and portable library able to perform real time
 contour detection. The library is implemented in  C++ with some bindings in python,
 making it relatively convivial to use for non-programmers.
To manage the edge detection during welding process,
the library is composed by four processing modules: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, 
 heat and electrodes positions; the raw image registered by CCD 
 camera are not calibrated and present light inhomogeneities and 
 noise. In order to obtain the real shape and size of weld elements, this module 
 includes calibration algorithms. To detect the welding objects contours it is 
 necessary to improve the weld element image. This module has the 
 pre-processing treatments for noise reduction and image enhancement.
 Then to start the edges detection process, this module includes processing
 algorithms as segmentations by samples comparator, watershed transformation,
 filters edge detectors and histogram based methods.  
 Most of the functionality comes from \cite{OPENCV}.
\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
   segments to conclude the edge detection
  process, completing and in some cases extrapolating the weld
  elements edge. It is also responsible to compute the geometrical 
  data of welding elements such weld pool surface and metal transfer drop volumes. 
  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
  such as triangulations and mesh generation, alpha shape and 
  convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements
   it is necessary to extract the welding object edge from the image; this
   required some criteria such as continuity, length or closing condition.
   This module use graph algorithms to  identify and select the welding element edge using the
   criteria. This module is composed by connected segments, estimates
   minimal cut, determine largest chain segments and others algorithms. 
   The algorithm of \cite{BOOSTGRAPH} are used.
\item[Visualization:] This module is a set of 
  functions use to execute, show and/or register the 
  different steps at the image process.
\end{description}

@@

\subsection{ The Analyzing methods}
\label{ the_analyze_methods}
Image treatment and implemented algorithms are dependent of the optical setup and recording of images.
Nevertheless even if shadowgraphy technic is modified, the algorithm to detect and measure profile during
welding will still be valid by modifying some parameters.

\subsubsection{ Image Calibration}
\label{ image_calibration}

@@

\subsubsection{ Image Treatment}
\label{image_treatment}

@@

Then, an  adaptive threshold can be used to enhance the difference
between shadow elements and light zones. To the adaptive threshold it is important 
to choose the correct size region where it will be applied. Small regions to threshold
will generate isolated patterns (groups of pixels). Big regions will generate
a classical like threshold image \cite{SABER}. The region size dominium choose
to threshold application is $23\times 23\ pixels$. The threshold criteria 
choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
 $max(value)$ is the grey level value choose to identify the pixels above
threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
 before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
$threshold(x,y)$ is obtain by subtraction between the average grey level of region
 pixels neighborhood and a constant parameter $C_{threshold}$.  
Small edge defects can still be found, due to the previous smooth filter and some arc 
light interference regions, which are bigger than regions size to
threshold (see figure \ref{fig::photo-macro-drop-adaptivethreshold}).

@@

\subsubsection{Edge extraction}
\label{edge_extraction}
\textbf{Macrodrop}

@@

\textbf{Droplets}

To the droplet edge section, the white points cord defines 
the surface of the droplet. Note at figure \ref{fig::photo-droplet-canny} that the biggest closer
 cord correspond to the droplet section. The idea is to build segments around
 the cords, and take the longest closer segment.

@@

>>>>

\section{Image processing tools} 
\label{ image_processing_tools}

@@

A multipurpose image processing library has been developed 
and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different 
welding objects such as Macro drop, droplets and weld pool.
The library can manage
different kinds of image acquisition (optical setup). 
erCv is assembled in a oriented object C++ language.
Then,  erCv is a scalable 
and portable library able to perform real time
 contour detection. The library is implemented in  C++ with some bindings in python,
 making it relatively convivial to use for non-programmers.
To manage the edge detection during welding process,
the library is composed by four processing modules: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, 
 heat and electrodes positions; the raw image registered by CCD 
 camera are not calibrated and present light inhomogeneities and 
 noise. In order to obtain the real shape and size of weld elements, this module 
 includes calibration algorithms. To detect the welding objects contours it is 
 necessary to improve the weld element image. This module has the 
 pre-processing treatments for noise reduction and image enhancement.
 Then to start the edges detection process, this module includes processing
 algorithms as segmentations by samples comparator, watershed transformation,
 filters edge detectors and histogram based methods.  
 Most of the functionality comes from \cite{OPENCV}.
\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
   segments to conclude the edge detection
  process, completing and in some cases extrapolating the weld
  elements edge. It is also responsible to compute the geometrical 
  data of welding elements such weld pool surface and metal transfer drop volumes. 
  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
  such as triangulations and mesh generation, alpha shape and 
  convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements
   it is necessary to extract the welding object edge from the image; this
   required some criteria such as continuity, length or closing condition.
   This module use graph algorithms to  identify and select the welding element edge using the
   criteria. This module is composed by connected segments, estimates
   minimal cut, determine largest chain segments and others algorithms. 
   The algorithm of \cite{BOOSTGRAPH} are used.
\item[Visualization:] This module is a set of 
  functions use to execute, show and/or register the 
  different steps at the image process.
\end{description}

@@

\section{ The Analyzing methods}
\label{ the_analyze_methods}
Image treatment and implemented algorithms are dependent of the optical setup and recording of images.
Nevertheless even if shadowgraphy technic is modified, the algorithm to detect and measure profile during
welding will still be valid by modifying some parameters.

\subsection{ Image Calibration}
\label{ image_calibration}

@@

\subsection{ Image Treatment}
\label{image_treatment}

@@

Then, an  adaptive threshold can be used to enhance the difference
between shadow elements and light zones. To the adaptive threshold it is important 
to choose the correct size region where it will be applied. Small regions to threshold
will generate isolated patterns (groups of pixels). Big regions will generate
a classical like threshold image \cite{SABER}. The region size dominium choose
to threshold application is $23\times 23\ pixels$. The threshold criteria 
choose is binary: $grey\_level\_threshold(x,y) = max\_value$ if $grey\_level\_origin(x,y) >  threshold(x,y)$
or $grey\_level\_threshold(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
 $max\_value$ is the grey level value choose to identify the pixels above
threshold parameter, $grey\_level\_origin(x,y)$ is the grey level value of pixel
 before threshold and $grey\_level\_threshold(x,y)$ is the pixel grey level after threshold.
$threshold(x,y)$ is obtain by subtraction between the average grey level of region
 pixels neighborhood and a constant parameter $C_{threshold}$.  
Small edge defects can still be found, due to the previous smooth filter and some arc 
light interference regions, which are bigger than regions size to
threshold (see figure \ref{fig::photo-macro-drop-adaptivethreshold}).

@@

\subsubsection{Edge extraction}
\label{edge_extraction}
\begin{description}
\item[ Macrodrop]

@@

\item[ Droplet]
To the droplet edge section, the white points cord defines 
the surface of the droplet. Note at figure \ref{fig::photo-droplet-canny} that the biggest closer
 cord correspond to the droplet section. The idea is to build segments around
 the cords, and take the longest closer segment.

@@

\end{description}
